For submission to the Journal of Integrated Pest Management

### 2021-05-27 ofv_fife_2021.Rmd
Minor edit

The initial site of collection was visited two more times during 2020 to gather plants for identification of the unidentified plant pathogen. These surveys were conducted during July and August to collect more putatively infected plants, including more *Liriope* spp. as well as a new species which also belongs to the family Asparagaceae; *Aspidistra elatior* Blume, which was suspected to be infected due to unusually chlorotic leaves (`r citef("fig_2")`). Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification. 
The FDACS determined that the virus was *Orchid fleck dichorhavirus* using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015]. Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.

>>>>

The initial site of collection was visited two more times during 2020 to gather plants for identification of the unidentified plant pathogen. These surveys were conducted during July and August to collect more putatively infected plants, including more *Liriope* spp. as well as a new species which also belongs to the family Asparagaceae; *Aspidistra elatior* Blume, which was suspected to be infected, due to both its proximity to infected *Liriope* and its unusually chlorotic leaves (`r citef("fig_2")`). Upon collection, these new samples were sent to the Florida Department of Agriculture and Consumer Services (FDACS) for identification. 
The FDACS determined that the virus was *Orchid fleck dichorhavirus* using previously published primers and methods [@Kubo2006a; @Kubo2006b; @Kubo2009a; @Kubo2009b; @RamosGonzalez2015]. Orchid subgroup 1, OFV-Orc was identified following the methods described in @Kondo2017.
